\documentclass[12pt]{article}
%\usepackage{report}

\usepackage[utf8]{inputenc} % allow utf-8 input
%\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
%\usepackage{microtype}      % microtypography
\usepackage{lipsum}		% Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{footnote}
\usepackage{doi}
\usepackage{comment}
\usepackage{multirow}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{float}
\usepackage{amsmath}
%\usepackage{subfigure}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage[skip=10pt plus1pt]{parskip} %I got rid of indent=30pt to make the paragraphs line up nicer - GI
\usepackage[top=3cm, bottom=5cm, left=2.5cm, right=2.5cm]{geometry}

\title{Flash Floods notes dump}
\author{:D}
\begin{document}
\maketitle
\section{description}
You are asked to develop a model for the formation of a flash flood in a watercourse (e.g.
a river, stream, canal). These can be particularly dangerous in desert areas, particularly in
canyons. This is primarily because large amounts of rain can fall within a short period on
poorly drained soil. A surprising feature of such flash floods is that they can occur almost
instantaneously many miles away from the area of the rainfall. You should use your model
to understand how such sudden rises in water level can occur.

You are to write a report (no more than 10 pages long) that describes the mathematical
modelling associated with determining how flash flooding occurs. The usual report format
should be followed, i.e the report should contain a short introduction to the problem and
then proceed to indicate the modelling steps you and your group have undertaken. The
report should summarise the results of your group discussions giving careful attention to the
explanations of the assumptions you have made to create the models, the variables that you
used and the equations you studied. You should give a discussion of the implications of your
modelling results for the physical problem. Include a brief discussion of additional physical
factors you might include to further improve the predictions and how you might put these
into the mathematical model.
\section{week 1}
\begin{itemize}
    \item to do: find l(A) for different cross sections
box canyon, wedge (closer to what a riverbed is), parabola, etc. investigate effect on shape
    \item plot solutions and find shock
\end{itemize}

\section{Approxiations/assumptions}
Using Darcey-Weisbach equations, friction factor is between 0.03-0.08 (https://doi.org/10.1016/j.mex.2022.101669) (Darcey Weisbach is a theoretical model for an open topped channel. We use it as we're generalising - something like the Manning factor could be empirically determined for a specific river.)

Flash flooding commonly happens more where rivers are narrow and steep, so they flow more quickly. It can also occur from small rivers in built-up urban areas, where hard surfaces such as roads and concrete don't let the water drain away into the ground. This leads to surface overflow and can often overwhelm local drainage systems, leading to flash flooding.

$\alpha$ is about 2$\%$
The world-average river slope is about $2\%$ (i.e. 2m/km), less than $1\%$ is gentle and more than $4\%$ is steep.
High gradient streams tend to be wedge shaped.


Assuming rain distribution is gaussian, is volume of water

We want area the rainfall happened over and how far from the river
\section{week3 }
\textbf{important! final version of characteristic_plot.py pushed. feel free to make changes to your local version.}
\end{document}



